Characteristic polynomial of p-adic matrices

### 2017-01-25 charpoly/charpoly.tex
Minor improvements and biblio

>>>>

We recall some of the definitions and results of \cite{CRV:2014}
as a foundation for our discussion of the precision for the characteristic polynomial
of a matrix.  We will be concerned with two $K$-manifolds in what follows:
the space $M_n(K)$ of $n \times n$ matrices with entries in $K$ and the space
$K_n[X]$ of monic degree $n$ polynomials over $K$.  Given a matrix $M \in M_n(K)$,
the most general kind of precision structure we may attach to $M$ is a
\emph{lattice} $H$ in the tangent space at $M$.  However, representing an
arbitrary lattice requires $n^2$ basis vectors, each with $n^2$ entries.  We therefore
frequently work with certain classes of lattices, either \emph{jagged} lattices
where we specify a precision for each matrix entry or \emph{flat} lattices where
every entry is known to a fixed precision $O(p^m)$.  Similarly, precision for
monic polynomials can be specified by giving a lattice in the tangent space
at $f(X) \in K_n[X]$, or restricted to jagged or flat precision in the interest
of simplicity.

The main benefit of working with lattices is the following result
\citelist{\cite{CRV:2014}*{Lem. 3.4} \cite{CRV:2015}*{Prop. 2.2}}.
